Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-05-22 doc/lean.tex
Added cross reference

\begin{theorem}
\label{thm:lean:equiv}
If the proof checker has assembled POG $P$ with root node $\noder$ starting from input formula $\inputformula$, and \textsc{final conditions} hold of the checker state, then $\inputformula$ is logically equivalent to $\phi_\noder$.
\end{theorem}
\begin{proof}
\textsc{Final conditions} imply that the active clausal formula $\theta$ is exactly $\pogformula \doteq \{\{r\}\} \cup \; \bigcup_{\nodeu \in P} \theta_{u}$. The conclusion follows from this and the checker invariants. The full proof is formally verified in Lean.
\end{proof}
After certifying a CPOG proof, the checker can pass its in-memory POG representation to the ring evaluator. We can conclude that this is partitioned directly from \texttt{invariants.partitioned}.

>>>>

\begin{theorem}
\label{thm:lean:equiv}
If the proof checker has assembled POG $P$ with root node $\noder$ starting from input formula $\inputformula$, and \textsc{final conditions} (as stated in Section~\ref{subsection:semantics}) hold of the checker state, then $\inputformula$ is logically equivalent to $\phi_\noder$.
\end{theorem}
\begin{proof}
\textsc{Final conditions} imply that the active clausal formula $\theta$ is exactly $\pogformula \doteq \{\{r\}\} \cup \; \bigcup_{\nodeu \in P} \theta_{u}$. The conclusion follows from this and the checker invariants. The full proof is formally verified in Lean.
\end{proof}
After certifying a CPOG proof, the checker can pass its in-memory POG representation to the ring evaluator. We can conclude that this is partitioned directly from \texttt{invariants.partitioned}.
